SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.95$

### 2020-03-09 Paper/ms.tex

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Paper/Figures/snrequiem_w0wa_compared_to_lsst_wfirst.pdf}
    \caption{The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$). Contours show the 1$\sigma$ confidence region for a typical sample of lensed SN time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta). Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation. In order to isolate the $w_0, w_a$ dependence, all contours are constructed assuming perfect knowledge of $H_0$, $\Omega_{m,0}$ and $\Omega_{\rm de,0}$.  SN Requiem could be highly complementary to the LSST+WFIRST lensed SN sample, due to its unusual combination of a relatively low-redshift lens ($z=0.338$) and high-redshift source ($z=1.95$). \SR{TBD: make the contours actually reflect realistic confidence regions for LSST, WFIRST and SN Requiem}. }
    \label{fig:my_label}
\end{figure}
